Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-11 syntaxsemantics.tex
+

  Definition store (mem: $\sigma.\mathcal{M}$) (w: { w: word 64 | aligned w }) (v: word 64):mem64 * (unit + MemFail) :=
    match $\sigma$.mem !! (pfn (proj1_sig w)) mem with
      | None =>
        (($\sigma.\mathcal{M}$<[(pfn (proj1_sig w)) := 
             (inl (fun off =>
                  if (word_dec off (page_off (proj1_sig w))) then v else zero 64))]> mem
         ), inl tt)
      | Some (inl page) => (* update page contents *)
        (($\sigma.\mathcal{M}$<[(pfn (proj1_sig w)) := 
             (inl (fun off =>
                  if (word_dec off (page_off (proj1_sig w))) then v else zero 64))]> mem
         ), inl tt)
      | Some (inr fault) => (mem, inr fault)
    end.

  Program Definition pfn (w : word 64) := shift_dropn w 12 _.
  Program Definition page_off (w : word 64) := bottomn w 12 _.
\end{lstlisting}
with frame and offset masking applied on the physical address being loaded. As expected \textsf{store} would be the update on the memory map entry
\todo[inline,color=yellow]{Colin, could you mention that we simplified the maps here to get rid of MemFail?}
After defining the translation in terms of physical load and store action, now we can define our \lstinline|mov| instructions.
STOP HERE

>>>>

  Definition store (mem: $\sigma.\mathcal{M}$) (w: { w: word 64 | aligned w }) (v: word 64):mem64 * (unit + MemFail) :=
    match $\sigma$.mem !! (pfn (proj1_sig w)) mem with
      | None =>
        (($\sigma.\mathcal{M}$<[(pfn (proj1_sig w)) := (inl (fun off =>
           if (word_dec off (page_off (proj1_sig w))) then v else zero 64))]> mem), inl tt)
      | Some (inl page) => (* update page contents *)
        (($\sigma.\mathcal{M}$<[(pfn (proj1_sig w)) := (inl (fun off =>
           if (word_dec off (page_off (proj1_sig w))) then v else zero 64))]> mem), inl tt)
      | Some (inr fault) => (mem, inr fault)
  Program Definition pfn (w : word 64) := shift_dropn w 12 _.
  Program Definition page_off (w : word 64) := bottomn w 12 _.
with frame and offset masking applied on the physical address being loaded. As expected \textsf{store} would be the update on the memory map entry
\todo[inline,color=yellow]{Colin, could you mention that we simplified the maps here to get rid of MemFail?}
After defining the translation in terms of physical load and store action, now we can define our \lstinline|mov| instructions.
